---
title: "Subset Polygons"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sf)
library(tidyverse)

hartford <- st_read("C:/Users/gioc4/Desktop/hartford.shp")
cfs <- st_read("C:/Users/gioc4/Desktop/cfs.shp")

```

## Subset Polygons

This is a bit of code intended to mimick the existing ESRI [subset polygons ](https://pro.arcgis.com/en/pro-app/latest/tool-reference/geostatistical-analyst/generate-subset-polygons.htm)
function. The intended use is obtaining non-overlapping polygons with an equal 
number of points in each area. The general algorithm is:

1. Use iterative nearest neighbors to identify equal sized clusters
2. Create a thiessen tessellation around all points
3. Merge and dissolve thiessen polygons by cluster id

## Example

Here is an example using a random sample of calls for service data from 
Hartford, CT in 2020. The goal is to identify 8 patrol areas with an equal number 
of calls for service. Here, we can specify g = 8 for eight groups, and then add
the point `p` and polygon `a` shapefiles. 

```{r, message=FALSE, warning=FALSE}
library(sf)
library(tidyverse)

source("C:/Users/gioc4/Dropbox/subset_polygons/subset_polygons.R")

# find polygons that make 8 equal-sized groups
# based on calls for service
cfs_groups <- subset_polygons(p = cfs, 
                              a = hartford, 
                              g = 8, 
                              plot_map = T, 
                              data_return = "point")

# check size of groups
table(cfs_groups$grp)
```
